Hysteresis in human computation:\\ how one task affects another

### 2014-11-19 docs/publications/2014.09_SCIENCE/new_man.tex
proof read manuscript and improve theta plot

Microtask platforms combine the efforts of large numbers 
of people to perform tasks that are difficult to automate with computers 
alone.  These platforms support near-real-time task completion, mimicking a
compute server, and fundamentally shift the role of the human from consumer to 
producer of computing resources.  To realize its full
potential, we must understand how human computation differs from machine 
computation, and address the biases known to be inherent in 
human cognition.  The effects of various task-design variables on worker
performance have been investigated, but there has been little 
investigation into how consecutive tasks influence one another. Here we show 
that the responses in later tasks are strongly influenced by the content of 
earlier ones, an effect that is as strong or stronger than the effect of 
framing.  Our findings are not solely cautionary; we find
that these \textit{intertask effects} can be harnessed to improve the quality 
of responses, and thereby help to achieve expert-level judgments in citizen 
science and other crowdsourcing initiatives. 
As an ancillary contribution, we demonstrate the use of machine learning 
algorithms measure exposure-induced human bias, in terms of its ability to 
influence human computations. 
\end{sciabstract}

@@

But the ability to program with high-level human instructions comes with a 
cost: HPU output is inherently noisy.  Part of this noise can be explained
in terms of worker demography (\#).  But systematic cognitive biases also 
play a role (\#), a dimension of variability we investigate here.   
So far, investigation has explored such design factors as the level of 
pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, pre-screening of 
workers \cite{paolacci2010running}, and user-interface design 
\cite{Finnerty2013}.  Researchers have also investigated \textit{framing}, 
by testing the effects of describing the workflow context 
\cite{Kinnaird2012281}, the purpose of tasks 
\cite{chandler2013breaking}, or using alternate problem descriptions
\cite{thibodeau2013natural}.  To our knowledge, no study has investigated 
the influences that consecutive microtasks exert on one another.

It is known that people are susceptible to priming effects 
\cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
one task may depend in part on previous ones.  Such \textit{intertask} effects
would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
only a function of the current input, but also of the history of inputs, with
important implications for the design of crowdsourcing initiatives.

Here we describe a series of experiments using the Amazon Mechanical
Turk (MTurk) microtask platform in which we studied intertask effects
for image-labeling tasks.  Image-labeling tasks are among the most 
common kinds of microtasks
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, 
and it seems likely that this will remain the case in the long term because
they provide a source of ground truth in computer vision research 
\cite{5543192}.  
During the experiments, workers were presented with a series of images (one at
a time), and had to provide five descriptive words (\textit{labels}) for each.
We varied first five images (hereafter the \textit{initial tasks})
and observed the effect this had on the workers' labels for the last five
(\textit{test tasks}).

The initial tasks were chosen to embed a certain \textit{prime concept}.
In our first experiment, our prime concepts were \textit{food} and (non-food) 
\textit{objects}.  In our second experiment, the prime concepts were 
\textit{food} and \textit{culture}.  The test tasks for the experiments used 
images that combined both prime concepts. Any given worker performed in only 
one experiment, and was randomly assigned initial tasks based on one of the 
prime concepts.  From the perspective of the worker, we made no distinction 
between the initial tasks and test tasks.

@@

We found that intertask effects were stronger than framing, unless the worker
was required to echo the frame, in which case both exposures were on par.  
Our results demonstrate that initial tasks can change 
workers' focus in later tasks.  We also found that intertask effects 
significantly altered the level of specificity, and the diversity of 
vocabulary that workers used, and did so in ways that differed from framing.
Contrary to our initial expectations, our findings suggest that the HPU 
programmer can leverage intertask effects.  By carefully designing workflows,
worker focus, specificity, and expressivity can be tuned.  Our 
findings carry two lessons for the task designer: intertask
effects can severely bias HPU output if uncontrolled, but if properly 
controlled, intertask effects might be optimized, which may be of significant 
utility in achieving expert-level output.

\paragraph*{Measuring computational hysteresis.}
Before describing the details of our experiments, we explain some 
choices made in measuring intertask and framing effects 
(hereafter collectively \textit{exposure effects}).  
It might be tempting to invoke the concept of a ``neutral frame of mind'' 
which would serve as a baseline for drawing comparisons.  But such a concept 
seems both difficult to define, and unlikely to arise.
Therefore, we instead always consider the effect of one exposure 
\textit{relative} to another.  Thus, our experiments consist of 
pairs of treatments between which we can make meaningful comparisons.

@@

For this reason, we develop a measure in which we train classifier algorithms 
to infer the exposure of an HPU from its outputs.
If a classifier infers an HPU's exposure with significantly 
better accuracy than provided by chance, then the HPU outputs must have 
been affected by the exposure.  
But in addition, the classifier serves as a kind of certificate, since it is 
an example of an algorithm whose path of execution is influenced by the 
exposure of 
individual HPUs.  In the supplementary material, we ground our approach 
rigorously in terms of the L1-distance metric, which is a measure of 
divergence between distributions.  The L1-distance ranges from 
0 to 1.  In our case, a value of 1 indicates that the HPU's exposure
influences its output so strongly that the exposure can be inferred from the
output without ambiguity.  A value of 0 indicates that the exposure has no
impact on the HPU's outputs.  The connection between the
L1-distance, $D_\mathrm{L1}$, and a classifier's accuracy, $\eta$, is given by:
\begin{equation}
	D_\mathrm{L1} \geq 2 \eta - 1, 
	\label{l1}
\end{equation}
Since a classifier's performance provides a lower bound on the L1-distance, 
we shall denote $D_\mathrm{L1}^-\equiv 2\eta-1$.
The L1-distance admits the following interpretation: if two distributions
$P$ and $Q$ have an L1-distance $d$, then in the worst case, the 
frequency with which a binary algorithm operating on samples
from $P$ outputs a 1, will differ from that when operating on samples from 
$Q$ by $d \times 100\%$.  
Thus, we can interpret $D_\mathrm{L1}^-$ as a kind of
lower bound for the worst-case bias induced by HPU hysteresis.
We provide further discussion of the statistical properties of our approach 
in the supplementary material.

\paragraph{Experimental setup.}
\begin{figure}
	\centering
	\includegraphics[scale=0.7]{figs/images.jpg}
	\caption{
		Examples of images used in labeling tasks. Images from initial
		tasks: A) \textit{task1:food}, B) 
		\textit{task1:obj}, D) \textit{task2:food}, 
		E) \textit{task2:cult}.  Images from  test tasks: C) \textit{exp1}, 
		F) \textit{exp2}.  The full set of experimental materials is 
		shown in the supplementary material.
	}

	\label{fig:task}
\end{figure}
We performed two experiments, soliciting respectively 2300, and 900 MTurk 
workers to label images depicting food, kitchen- and dining-ware, and cultural
scenes.  In a given experiment, all workers performed the same test
tasks, the output of which was our main dependent variable.  Before performing
the test tasks, workers were subjected to an exposure, via one of 
two \textit{modalities}: either they completed a set of initial tasks, or 
were exposed to a frame, or both.  As mentioned, from the perspective of the worker, 
there was no distinction or discontinuity between initial and test tasks.

@@

Note that food and objects are both relatively well-defined classes of 
physical entities.  To explore a different conceptual axis, in 
\textit{exp2} we adopted the prime concepts food and \textit{culture}.
Compared to food and objects, culture is more abstract, difficult to define, 
and, rather than comprising a class of physical entities, it encapsulates
sets of beliefs, values, and practices.  Examples of images from the initial 
tasks in \textit{task2} are shown in Fig.~\ref{fig:task}, and the full 
collection of 
experimental materials is presented in the supplementary material.  We 
ensured that workers only participated in one treatment of one experiment.

\setlength{\tabcolsep}{3pt}
\begin{table}[t]
\centering
\begin{tabular}{ c c c c c }
		\hline \noalign{\smallskip}
		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.6cm}{\centering \textbf{Framing\\ Prime}} & \parbox[c]{1.7cm}{\centering \textbf{Initial\\ image set}}	\\

@@

		\multirow{6}{*}{ \parbox[c]{1cm}{ \phantom{XXX} exp1}} 
			& \multirow{2}{*}{task1} & food & none & food\\
			& & obj & none & objects\\

@@

	\caption{ \footnotesize{ 
		We use the treatment names shown to refer to specific sections of 
		the data collected.  For example, \textit{task2:food} refers to the
		treatment in the second experiment which was not exposed to a frame, 
		and whose initial tasks contained images of food (7th row).
	}}
	\label{table:1}
\end{table}

@@

We assessed the strength of intertask and framing effects
by training a multinomial naive Bayes classifier to infer a worker's exposure
based on the labels provided in the test tasks (see Fig.~\ref{fig:theta}).
This inference was made over the two possibilities given the treatment pair
to which the worker had been assigned.
We found that in \textit{task1}, whether a worker performed food- or 
object-containing initial tasks, had a strong effect on their subsequent 
labels, introducing a bias that probably exceeds 30\%.  In comparison, the 
framing effect in \textit{frame1} did 
not influence workers' labels enough for the classifier to make predictions 
with significantly better accuracy than that afforded by chance.  The results 
for \textit{exp2} show a similar, but even more pronounced trend, with the bias
induced by intertask effects in \textit{task2} probably exceeding 50\%.

We see a comparable effect size in the \textit{echo} treatment pair.
We expected \textit{echo} to show a very strong effect because, by requiring
the worker to echo the purported purpose of the task, we signal that it
is of particular importance, more so than the instructions provided
beforehand.  The fact that the intertask effects were on par with the framing 
effects in \textit{echo} shows just how powerful intertask effects can be.

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Lower-bound estimates for the  worst-case bias introduced in image
		labeling tasks due to worker exposure effects.  The estimate was 
		based on the performance of a multinomial naive Bayes classifier,
		trained to infer an HPUs exposure. A) bias induced through various
		modalities and prime concepts (see Table 1). B) Bias induced in 
		\textit{task1}, as a function of test task position.  Error bars
		show the one-tailed 95\% confidence interval.
	}
	\label{fig:theta}
\end{figure}

\paragraph{Dynamics of intertask effects.} It is natural to expect 
intertask effects to attenuate as a worker proceeds through test tasks.  
In \textit{task1}, we permuted the test tasks, allowing us to 
measure intertask effects as a function of test task position, while factoring
out the content-dependant differences between test tasks
(see Fig.~\ref{fig:theta}B). 
We found intertask effects were most pronounced for the first test image,
dropping off substantially for the second test task, but maintaining a 
significant effect through until the 5th test task.  
This shows that the range of intertask effects extend accross at least 5 
tasks, and probably substantially more.
This makes intertask effects of greater concern, but as we will show, it also
makes intertask effects of greater potential utility.
In future work, it would be interesting to investigate whether a worker's
susceptibility to intertask effects varies accross a large batch.  For example,
It is conceivable that the first few tasks induce especially strong
or long-lasting effects, in effect ``setting the tone'' for the rest of the batch.

\paragraph{Detailed influences on worker outputs.} 
\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/vocab_specificity.pdf}
	\caption{
		Detailed exposure effects on workers label vocabulary, for various
		exposure modalities and prime concepts (see Table 1).  A) Change in 
		the number of food-related labels used. B) Change in the total number 
		of \textit{unique} food-related labels used. C) Relative specificity
		of treatment pairs, when considering food-related labels.  For all
		plots, a positive bar height indicates an increase for the 
		food-exposed treatment.
	}
	\label{fig:specificity}
\end{figure}

@@

Using an augmented hypernym-hyponym structure of wordnet to identify nouns 
depicting food, we found that, for the experimental pairings in 
\textit{exp1}, the
food-exposed treatments did produce a significantly larger fraction of 
food-related labels (see Fig.~\ref{fig:specificity}A).  While the shift in 
focus with regard to food does help explain the classifier's ability to 
infer workers exposure, it still leaves most of this difference unexplained 
(*).
Furthermore, such a simple relationship cannot explain the observation for
\textit{exp2:task2} where we see a significant but reversed effect
(see Fig.~\ref{fig:specificity}A).
Given the difference between the food-culture and food-object axes, it should
not be surprising that the effect of exposure is different.  We must therefore
be prepared to accomodate multiple, countervailing factors which influencing 
the bulk number of references to the prime concept (food).  We will come back 
to this notion momentarily.

To explore these effects further, we looked more closely at which particular
labels are most suppressed (activated) by a worker's exposure.  Remarkably,
we found that, for all treatment pairs, ``food'' was always the most 
suppressed label among 
the food-exposed workers.  This is surprising, considering 
that the bulk incidence of food-related labels mostly \textit{increased} among 
food-exposed workers.  But taken together, the increase in references to food 
and the decrease in the incidence of ``food'' per se (which is the most generic
food-reference in the wordnet-based ontology), necessarily implies that
food-exposed workers have traded ``food'' for more specialized references to 
food.

In a crowdsourcing task, considerable effort must be given to shaping the 
vocabulary with which a worker engages a task.  To draw an example from the 
domain of citizen science, in galaxy zoo, workers catalog images of galaxies 
in terms of smoothness, and the presence of rings, dust lanes, digital 
disturbances, and so on.  Shaping this vocabulary is crucial to the reliability
of results.  In galaxy zoo, the interface contstrains and prompts the user
with this basic vocabulary.  But this would not appear to be sufficient, since
a set of positive and negative training examples are used, together with
peer-to-peer and peer-to-expert exchange in discussion areas, presumably to
refine and homogenize the vocabulary (\#).

In our set-up, where the worker's vocabulary is unconstrained, we can 
directly observe the effects that frames and initial tasks have on worker 
vocabulary.  By looking at the number of unique food-related labels that 
workers produced, we assessed the richness of vocabulary that workers used when
referring to food (see Fig.~\ref{fig:specificity}B.  We found that the 
food-exposed workers use a richer vocabulary of 
food-related words, even in cases like \textit{task2:food}, where they 
made fewer references to food overall.  
Interestingly, task-based exposure to food had a stronger enriching effect 
(for food-vocabulary) than did framing-based exposures. (* explain why vocab 
diversity is useful.)

Using the ontology of food induced by wordnet, we were able to directly
calculate the relative specificity of workers from different treatments.
To do this, we considered all the labels from one treatment
(for example \textit{task1:food}) and compared these to all the labels from 
another (\textit{task1:obj}).  For all possible comparisons, we observed 
which treatment's label was more specific more often, and normalized this
quantity as a percentage (we provide greater detail in the supplementary 
material).

@@

Taken together, the results presented in Fig.~\ref{fig:specificity} can 
be explained by a combination of priming and a context-dependant appraisal
of salience resembling \textit{negative} priming.
Negative priming occurs when a repeated stimulus, which is perceived to be
non-salient, begins to be ignored.

We propose that, as a worker from \textit{task1:food} proceeds through the 
initial tasks, food-related memories and concepts are activated, increasing 
the likelihood that she uses a variety of food-related labels.  This accounts
for the overall increases the number of food-related labels, as well as the 
richness and specificity of her food-related vocabulary.  At the same time,
the fact that the images contain food at all begins to appear non-salient 
since due to its constancy, suppressing the most generic labels, such as 
``food''.  Thus, there is a simultaneous emphasis of the specialized 
references to the prime concept and de-emphasis of generic references.

This view accounts for the observation that there are fewer
food-related references overall in \textit{task2:food} compared to 
\textit{task2:cult}.  Workers in \textit{task2:food} are primed to use
specialized food references and negatively primed against using generic
ones.  Then, when workers encounter images with much more prominent 
cultural content in the test tasks, they attends to this novel content, 
decreasing the balance of food references.  
Meanwhile, workers in 
\textit{task2:cult} experience novelty from the introduction of food-oriented 
content, and, attending to it, drive the relative difference in the quantity 
of food-related labels further negative in in Fig.~\ref{fig:specificity}A.

Based on these observations, we submit the following ideas for consideration 
by the designers of crowdsourced initiatives.
\begin{enumerate}
	\item{
		Training tasks should be preferred over examples, since the immediate
		active use of information appears to increase its impact.
	}
	\item{
		Training tasks should contain the same distribution of 
		noise (or ``distracting features''), as the real dataset.
		Exposing workers to irrelevant features and identifying them as such
		will help direct focus toward salient features by virtue of
		negative priming.
	}
	\item{
		\textit{Validation tasks}, for which the correct output is known,
		are often used as a quality control measure.
		These should be dually considered as \textit{calibration tasks}, and
		should be designed to help worker to maintain an optimally primed 
		state. Feedback, for both correct and incorrect responses, 
		may further reinforce salient features.
	}
	\item{
		In many applications, such as the detection of pre-ictal 
		(pre-seizure) EEG traces, workers encounter few positive examples
		(most traces are not pre-ictal).  In the absence of positive examples,
		the target concept may degrade or drift.
		Drawing calibration tasks drawn from the underrepresented class may 
		help sustain the target concept.
	}
	\item{
		For the most precise classifications, it may be helpful to
		begin with a coarse classification.  For example, workers could 
		initially choose from  \texttt{class 0}, \texttt{class 1}, and 
		\texttt{borderline}.  Following the coarse classification, the 
		\texttt{borderline} examples could be batched together, allowing 
		workers to focus on finer distinctions which are only salient for fine 
		distinctions.
	}
\end{enumerate}

These techniques follow logically from our observations, but they are educated 
guesses.  We leave their direct testing to future work.

>>>>

Microtask platforms combine the efforts of large numbers 
of people to perform tasks that are difficult to automate with computers 
alone.  These platforms support near-real-time task completion, mimicking a
compute server, and shift the role of the human from consumer to 
producer of computing resources.  To realize its full
potential, we must understand how human computation differs from machine 
computation, and address the biases inherent in 
human cognition.  The effects of various task-design variables on worker
performance have been investigated, but there has been little 
investigation into how consecutive tasks influence one another. Here we show 
that the responses in later tasks are strongly influenced by the content of 
earlier ones, an effect that is as strong or stronger than the effect of 
framing.  Our findings are not solely cautionary; we find
that these \textit{intertask effects} can be harnessed to improve the quality 
of responses, and might thereby help to achieve expert-level judgments in 
citizen science and other crowdsourcing initiatives. 
As an ancillary contribution, we demonstrate the use of machine learning 
algorithms measure exposure-induced human bias, in terms of its ability to 
influence human computations. 
\end{sciabstract}

@@

But the ability to program with high-level human instructions comes with a 
cost: HPU output is inherently noisy.  Part of this noise can be explained
in terms of worker demography (\#).  But systematic cognitive biases also 
play a role (\#).   
So far, investigation has explored how worker performance is influenced by
such design factors as the level of 
pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, pre-screening of 
workers \cite{paolacci2010running}, and user-interface design 
\cite{Finnerty2013}.  Researchers have also investigated \textit{framing}, 
by testing the effects of describing the workflow context 
\cite{Kinnaird2012281}, the purpose of tasks 
\cite{chandler2013breaking}, or using alternate problem descriptions
\cite{thibodeau2013natural}.  To our knowledge, no study has investigated 
the influences that consecutive microtasks exert on one another.

It is known that people are susceptible to priming effects 
\cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
one task may depend on previous ones.  Such \textit{intertask} effects
would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
only a function of the current input, but also of the history of inputs, with
important implications for the design of crowdsourcing initiatives.

Here we describe a series of experiments, using the Amazon Mechanical
Turk (MTurk) microtask platform, in which we studied intertask effects
for image-labeling tasks.  Image-labeling tasks are among the most 
common kinds of microtasks
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, 
and it seems likely that this will remain the case in the long term because
they provide a source of ground truth in computer vision research 
\cite{5543192}.  
During the experiments, workers were presented with a series of images (one at
a time), and had to provide five descriptive words (\textit{labels}) for each.
We varied first five images (hereafter the \textit{initial tasks})
and observed the effect this had on the workers' labels for the last five
(\textit{test tasks}).

The initial tasks were chosen to embed a certain \textit{prime concept}.
In our first experiment, our prime concepts were \textit{food} and (non-food) 
\textit{objects}.  In our second experiment, the prime concepts were 
\textit{food} and \textit{culture}.  The test tasks for the experiments used 
images that combined both prime concepts used in the initial tasks. Workers 
participated in only one treatment of one experiment, and were randomly 
assigned initial tasks based on one of the 
prime concepts.  From the perspective of the worker, we made no distinction 
between the initial tasks and test tasks.

@@

We found that intertask effects were stronger than framing, unless the worker
was required to echo the frame, in which case the effects of both exposures were on par.  
Our results demonstrate that initial tasks can change 
workers' focus in later tasks.  Using the wordnet corpus, we analyzed 
the effects on the vocabulary used by workers when 
labeling test tasks. 
Exposure to both framing and initial tasks significantly altered the 
diversity of vocabulary that workers used when refering to the prime concept,
as well as the degree to which workers used specialized (rather than generic) 
words.

Contrary to our initial expectations, our findings suggest that the HPU 
programmer can leverage intertask effects.  By carefully designing workflows,
it is possible to tune worker focus, specificity, and expressivity.  Our 
findings carry two lessons for the task designer: intertask
effects can severely bias HPU output if uncontrolled, but if properly 
controlled, intertask effects might be of significant utility in achieving 
expert-level output.

\paragraph*{Measuring computational hysteresis.}
Before describing the details of our experiments, we explain some 
choices made in measuring intertask and framing effects 
(hereafter collectively \textit{exposure effects}).  
In trying to establish a mesure of exposure effects, it might be tempting to 
invoke the notion of a ``neutral frame of mind'' to serve as a baseline. 
But such a concept seems both difficult to define, and unlikely to arise.
Therefore, we always consider the effect of one exposure 
\textit{relative} to another.  We organized our experiments 
into pairs of treatments, between which it is possible to make meaningful 
comparisons.

@@

We developed a more stringent measure in which we train classifier algorithms 
to infer the exposure of an HPU from its outputs.
If a classifier infers an HPU's exposure with significantly 
better accuracy than provided by chance, then the HPU outputs must have 
been affected by the exposure.  
But in addition, the classifier serves as a kind of certificate, since it is 
an example of an algorithm whose path of execution is influenced by the 
exposure of 
individual HPUs.  In the supplementary material, we ground our approach 
rigorously in terms of the L1-distance metric, which is a measure of 
divergence between distributions.  The L1-distance ranges from 
0 to 1.  In our case, a value of 1 indicates that the HPU's exposure
influences its output so strongly that the exposure can be inferred from the
output without ambiguity.  A value of 0 indicates that the exposure has no
impact on the HPU's outputs.  The connection between the
L1-distance, $D_\mathrm{L1}$, and a classifier's accuracy, $\eta$, is given by:
\begin{equation}
	D_\mathrm{L1} \geq 2 \eta - 1, 
	\label{l1}
\end{equation}
Since a classifier's performance provides a lower bound on the L1-distance, 
we shall denote $D_\mathrm{L1}^-\equiv 2\eta-1$.
The L1-distance admits the following interpretation: if two distributions
$P$ and $Q$ have an L1-distance $d$, then in the worst case, the 
frequency with which a binary algorithm operating on samples
from $P$ outputs a 1, will differ from that when operating on samples from 
$Q$ by $d \times 100\%$.  
Thus, we can interpret $D_\mathrm{L1}^-$ as a kind of
lower bound for the worst-case bias induced by HPU hysteresis.
We provide further discussion of the statistical properties of our approach 
in the supplementary material.

\paragraph{Experimental setup.}
\begin{figure}
	\centering
	\includegraphics[scale=0.7]{figs/images.jpg}
	\caption{
		Examples of images used in labeling tasks. (The italicized treatment 
		names that follow are defined in Table \ref{table:treatments}.) Images 
		from initial tasks: A) \textit{task1:food}, B) 
		\textit{task1:obj}, D) \textit{task2:food}, 
		E) \textit{task2:cult}.  Images from  test tasks: C) \textit{exp1}, 
		F) \textit{exp2}.  The full set of experimental materials is 
		shown in the supplementary material.
	}

	\label{fig:task}
\end{figure}
We performed two experiments, soliciting respectively 2300, and 900 MTurk 
workers to label images depicting food, kitchen- and dining-ware, and cultural
scenes.  In a given experiment, all workers performed the same test
tasks, the output of which was our main dependent variable.  Before performing
the test tasks, workers were subjected to an exposure, via two 
\textit{modalities}: either they completed a set of initial tasks, or 
were exposed to a frame, or both.  As mentioned, from the perspective of the worker, 
there was no distinction or discontinuity between initial and test tasks.

@@

Note that food and objects are both relatively well-defined classes of 
physical entities.  To explore a different conceptual axis, in 
\textit{exp2} we adopted the prime concepts \textit{food} and \textit{culture}.
Compared to food and objects, culture is more abstract, and, rather than 
comprising a class of physical entities, it encapsulates
sets of beliefs, values, and practices.  Examples of images from the initial 
tasks in \textit{task2} are shown in Fig.~\ref{fig:task}, and the full 
collection of 
experimental materials is presented in the supplementary material.  We 
ensured that all workers only participated in one treatment of one experiment.

\setlength{\tabcolsep}{3pt}
\begin{table}[t]
\centering
\begin{tabular}{ c c c c c }
		\hline \noalign{\smallskip}
		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.6cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\

@@

		\multirow{6}{*}{ \parbox[c]{0.7cm}{ \phantom{XXX} exp1}} 
			& \multirow{2}{*}{task1} & food & none & food\\
			& & obj & none & objects\\

@@

	\caption{ \footnotesize{ 
		We use the treatment names shown to refer to specific sections of 
		the data collected.  For example, \textit{task2:food} refers to the
		treatment in the second experiment which was not exposed to a frame, 
		and whose initial tasks contained images of food (7th row).
	}}
	\label{table:treatments}
\end{table}

@@

We assessed the strength of intertask and framing effects
by training a multinomial naive Bayes classifier to infer a worker's exposure
based on the labels provided in the test tasks (see Fig.~\ref{fig:theta}).
This inference was made over the two possibilities for a given treatment pair.
We found that in \textit{task1}, whether a worker performed food- or 
object-containing initial tasks had a strong effect on their subsequent 
labels, introducing a bias that probably exceeds 30\%.  In comparison, the 
framing effect in \textit{frame1} did 
not influence workers' labels enough for the classifier to make predictions 
with significantly better accuracy than that afforded by chance.  The results 
for \textit{exp2} show a similar, but even more pronounced trend, with the bias
induced by intertask effects in \textit{task2} probably exceeding 50\%.

We see a comparable effect size in the \textit{echo} treatment pair.
We expected \textit{echo} to show a very strong effect because, by requiring
the worker to echo the purported purpose of the task, we signal that it
is of particular importance.  The fact that the intertask effects were on par with the framing 
effects in \textit{echo} shows just how powerful intertask effects can be.

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Lower-bound estimates for the  worst-case bias introduced in image
		labeling tasks due to worker exposure effects.  The estimate was 
		based on the performance of a multinomial naive Bayes classifier,
		trained to infer HPU exposures. A) Bias induced through various
		modalities and prime concepts (see Table 1). B) Bias induced in 
		\textit{task1}, as a function of test task position.  Error bars
		show the one-tailed 95\% confidence interval.
	}
	\label{fig:theta}
\end{figure}

\paragraph{Dynamics of intertask effects.} It is natural to expect 
intertask effects to attenuate as a worker proceeds through the test tasks.  
In \textit{task1}, we permuted the test tasks, allowing us to 
measure intertask effects as a function of task position, while factoring
out the content-dependant differences between tasks
(see Fig.~\ref{fig:theta}B). 
We found intertask effects were most pronounced for the first test task,
dropping off substantially for the second, but maintaining a 
significant effect through until the fifth test task.  
This shows that the range of intertask effects extends accross at least five 
tasks, and probably substantially more.
This makes intertask effects of greater concern, but as we will show, it also
makes intertask effects of greater potential utility.
In future work, it would be interesting to investigate whether a worker's
susceptibility to intertask effects varies accross a large batch.  For example,
It is conceivable that the first few tasks induce especially strong
or long-lasting effects, in effect ``setting the tone'' for the rest of the batch.

\paragraph{Detailed influences on worker outputs.} 
\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/vocab_specificity.pdf}
	\caption{
		Detailed exposure effects on workers' label vocabulary, for various
		exposure modalities and prime concepts (see Table 1).  A) Change in 
		the number of food-related labels used. B) Change in the total number 
		of \textit{unique} food-related labels used. C) Relative specificity
		of treatment pairs, when considering food-related labels.  For all
		plots, a positive bar height indicates an increase for the 
		food-exposed treatment for the pair indicated on the abscissa.
	}
	\label{fig:specificity}
\end{figure}

@@

Using the augmented hypernym-hyponym structure of wordnet to identify nouns 
depicting food, we found that, for the experimental pairings in 
\textit{exp1}, the
food-exposed treatments did produce a significantly larger fraction of 
food-related labels (see Fig.~\ref{fig:specificity}A).  While the shift in 
focus with regard to food does help explain the classifier's ability to 
infer worker exposures, it is insufficient to explain the observed performance
(*).
Furthermore, in \textit{exp2:task2} we see a significant but reversed effect
(see Fig.~\ref{fig:specificity}A), which suggests a more complicated 
relationship between exposure and label usage.
Given the difference between the food-culture and food-object conceptual axes, 
it should perhaps not be surprising that the effect of initial task exposure 
is different.  It would appear that we must be prepared to accomodate multiple 
countervailing factors influencing the number of references to the prime 
concept (food).  We will come back to this point momentarily.

To explore these effects further, we looked more closely at which particular
labels were most suppressed (activated) by a worker's exposure.  Remarkably,
we found that, for all treatment pairs, ``food'' was always the most 
suppressed label among 
the food-exposed workers.  This is surprising, considering 
that the overall incidence of food-related labels mostly \textit{increased} 
among food-exposed workers.  But taken together, the increase in references to 
food 
and the decrease in the incidence of ``food'' per se (which is the most generic
food-reference in the wordnet-based ontology), necessarily implies that
food-exposed workers have opted for more specialized references in place of 
``food''.

In a crowdsourcing task, considerable effort must be given to shaping the 
vocabulary with which a worker engages a task.  To draw an example from the 
domain of citizen science, in galaxy zoo, workers catalog images of galaxies 
in terms of \textit{smoothness}, and the presence of \textit{rings}, 
\textit{dust lanes}, \textit{digital disturbances}, and so on.  Shaping this 
vocabulary is crucial to the reliability of results.  The interface of
galaxy zoo helps by contstraining and prompting the user with this basic 
vocabulary.  But this would not appear to be sufficient, since
a set of positive and negative training examples are used, together with
peer-to-peer and peer-to-expert exchange in discussion areas, presumably to
further refine and standardize the vocabulary (\#).

In our set-up, where the worker's vocabulary is unconstrained, we can 
directly observe the effects that frames and initial tasks have on worker 
vocabulary.  By looking at the number of unique food-related labels that 
workers produced, we assessed the richness of vocabulary that workers used when
referring to food (see Fig.~\ref{fig:specificity}B).  We found that the 
food-exposed workers use a richer vocabulary of 
food-related words, even in cases like \textit{task2:food}, where they 
made fewer references to food overall.  
Interestingly, task-based exposure to food had a stronger enriching effect 
 than did framing-based exposures. (* explain why vocab 
diversity is useful.)

Using the ontology of food induced by wordnet, along with foods learned from
the Internet, we were able to directly calculate the relative specificity of 
workers from different treatments.
To do this, we considered all the labels from one treatment
(for example \textit{task1:food}) and compared these to all the labels from 
another (\textit{task1:obj}).  For all possible comparisons, we observed 
which treatment's label was more specific more often, and normalized this
quantity as a percentage (we provide greater detail in the supplementary 
material).

@@

Taken together, the results presented in Fig.~\ref{fig:specificity} can 
be explained by a combination of priming and  \textit{negative} priming.
Negative priming occurs when a repeated stimulus, which is perceived to be
non-salient, begins to be ignored (\#).

We propose that, as a worker from \textit{task1:food} proceeds through the 
initial tasks, food-related memories and concepts are activated, increasing 
the likelihood that she uses a variety of food-related labels.  This accounts
for the overall increases the number of food-related labels, as well as the 
richness and specificity of her food-related vocabulary.  At the same time,
since all images up to that point contained food, \textit{whether or not}
an image contains food begins to appear non-salient, suppressing the most 
generic references, such as ``food''.  Thus, there is a simultaneous emphasis of the specialized 
references to the prime concept and de-emphasis of generic references.

This view can account for the observation that there are fewer
food-related references overall in \textit{task2:food} compared to 
\textit{task2:cult}.  Workers in \textit{task2:food}, like those in 
\textit{task1:food}, are primed to use
specialized food references and negatively primed against using generic
ones.  Then, when these workers encounter the test tasks, with images 
containing more prominent cultural content, they attend to this novel content, 
decreasing their balance of food references.  
Meanwhile, workers in \textit{task2:cult}, having seen only cultural scenes,
experience novelty from the appearance of food-oriented content in the test 
tasks, and, attending to it, drive the relative difference in the quantity of 
food-related labels further toward the negative in in 
Fig.~\ref{fig:specificity}A.

Based on these observations, we submit the following ideas for consideration 
by the designers of crowdsourced initiatives.
\begin{enumerate}
	\item{
		Training tasks should be preferred over examples, since the immediate
		active use of information appears to increase its impact.
	}
	\item{
		Training tasks should contain the same distribution of 
		noise (or ``distracting features''), as the real dataset.
		Exposing workers to irrelevant features, and identifying them as such,
		will free up worker attention for salient features, by virtue of
		negative priming.
	}
	\item{
		\textit{Validation tasks}, for which the correct output is known,
		are often used as a quality control measure.
		These should be dually considered as \textit{calibration tasks}, and
		should be designed to help workers maintain an optimally primed 
		state. Feedback, for both correct and incorrect responses, 
		may further reinforce salient features.
	}
	\item{
		In many applications, such as the detection of pre-ictal 
		(pre-seizure) EEG traces, workers encounter few positive examples
		(most traces are not pre-ictal)(\#).  In the absence of positive 
		examples, the target concept may degrade or drift.
		Drawing calibration tasks from the underrepresented class may 
		help sustain the target concept.
	}
	\item{
		For the most precise classifications, it may be helpful to
		begin with a coarse classification.  For example, workers could 
		initially choose from  \texttt{class0}, \texttt{class1}, and 
		\texttt{borderline}.  Following the coarse classification, the 
		\texttt{borderline} examples could be batched together, allowing 
		workers to focus on features that are only salient for such fine 
		distinctions.
	}
\end{enumerate}

These recommendations follow logically from our observations, but they are 
educated guesses.  We leave their direct testing to future work.
